Analysis and results

### 2020-09-11 analysis/03_analysis.Rmd

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
  data = data,
  iter = 10000,
  thin = 5,
  seed = 42
)
run <- list(data = data, fit = fit)
if (intercept == 1) write_rds(run, here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) write_rds(run, here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

The following analysis follows specifying the model we'd like to evaluate. Note that the output of the model calibration is too large to push to GitHub.

@@

```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
# Load all model output
intercept_run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
public_affairs_run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
political_ideology_run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
social_views_run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
charity_voluntarism_run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
demographics_run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
public_political_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
public_political_social_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
public_political_social_charity_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
public_political_social_charity_demo_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

```{r extract-draws, eval=FALSE}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

# Load and extract data and model output
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit

@@

# Save draws
if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
```

@@

# Load draws
if (intercept == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
if (public_affairs == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))

>>>>

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
  data = data,
  iter = 10000,
  thin = 5,
  seed = 42
)
run <- list(data = data, fit = fit)
if (intercept == 1) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) write_rds(run, here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

The following analysis follows specifying the model we'd like to evaluate. Note that the output of the model calibration is too large to push to GitHub, but we can push the draws once we extract them.

@@

```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
# Load all model output
intercept_run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
public_affairs_run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
political_ideology_run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
social_views_run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
charity_voluntarism_run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
demographics_run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
public_political_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
public_political_social_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
public_political_social_charity_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
public_political_social_charity_demo_run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

```{r extract-draws, eval=FALSE}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 1 # + Demographics

# Load and extract data and model output
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit

@@

# Save draws
if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
```

@@

# Load draws
if (intercept == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "intercept.rds"))
if (public_affairs == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
